---
title: ""
author: ""
date: "8 de outubro de 2018"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(lme4)
library(ggthemes)
library(gsheet)
library(cowplot)
library(viridis)
library(lattice)
library(car)
library(janitor)
library(ggridges)
theme_set(theme_minimal())
```

# Data import

[Google sheet link]("https://docs.google.com/spreadsheets/d/1oBa_OIko04157D0-Z0tV7dN8BJxq9fAjEfbOkoSKy5s/edit?usp=sharing")


```{r}
sad <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1oBa_OIko04157D0-Z0tV7dN8BJxq9fAjEfbOkoSKy5s/edit?usp=sharing", sheetid = "all-data")
```

Total number of articles

```{r}
sad %>% 
  group_by(study) %>% 
  summarize(n()) %>% 
  nrow()

sad %>% 
    group_by(study) %>% 
  filter(Symptom_code != "NA") %>% 
  slice(1) %>% 
  tabyl(lesion_number) %>% 
  arrange(-n)

sad %>% 
    group_by(study) %>% 
  slice(1) %>% 
   filter(Symptom_code != "NA") %>% 
   tabyl(lesion_number, Symptom_code) %>% 
  pivot_longer(2:10, names_to = "code",
               values_to = "value") %>% 
  filter(value > 0)
```




# Article selection

We will use only studies that evaluated unaided and aided estimates. 

```{r}
sad %>% 
  group_by(study) %>% 
    filter(validation == "Unaided_aided") %>%
  summarize(n())
```


Now we select only those studies 

```{r}
sad_all <- sad %>% 
  filter(validation == "Unaided_aided") %>% 
     filter(!is.na(coefs)) %>% 
  filter(coefs != "R2") %>% 
   filter(coefs != "R2_CCC") %>% 
   filter(coefs != "R2_b")
```



Let's check now the number of studies again.


```{r}
sad_all %>% 
  group_by(study) %>% 
  summarize(n()) %>% 
  nrow()
```

## Transform variables

We need to do some corrections in the data and rename some variables

```{r}


# Obtain the Pearson's r from r-squared

sad_all <- sad_all %>%
  mutate(UN_r = sqrt(unaided_R2)) %>% 
  mutate(SAD_r = sqrt(aided_R2)) 

```


# Number of raters per study

```{r}
sad_all %>% 
   group_by(study, pub_year) %>% 
  tabyl(study) %>% 
  arrange(n) 

```

We want to remove studies with less than 5 raters to obtain better estimate 

```{r}
# remove studies with less than 6 raters
sad_all <- sad_all %>% 
  filter(study != 119,
         study != 127,
         study != 132,
         study != 147,
        study != 148,
        study != 152,
          study != 149,
        study != 150,
         study != 153,
         study != 46,
         study != 49,
         study != 33,
         study != 146,  
         study != 67,
         study != 100  
                  )

sad_all %>% 
  group_by(study) %>% 
  summarize(n()) %>% 
  nrow()
```

# Studies per organ

```{r}

sad_all %>% 
   group_by(study, organ) %>% 
  arrange(rater_id) %>%
  slice(1) %>%
  tabyl(organ)

sad_all <- sad_all %>% 
  mutate(organ2 = case_when(organ == "Leaf" ~ "Leaf",
                            TRUE ~ "Other"))


```

# Studies per pathogen 

```{r}
sad_all %>%
  group_by(study, pathogen_group) %>% 
  arrange(rater_id) %>%
  slice(1) %>%
  tabyl(pathogen_group) %>% 
  arrange(-n)
```


# Studies by diagram type

```{r}
sad_all %>%
  group_by(study, diag_type) %>% 
  arrange(rater_id) %>%
  slice(1) %>%
  tabyl(diag_type) %>% 
  arrange(-n)

sad_all <- sad_all %>% 
  mutate(diag_type2 = case_when(diag_type == "Drawing" ~ "Drawing",
                              TRUE ~ "Photo"))
```

# Studies by number of diagrams

```{r}
sad_all %>%
  group_by(study, n_diagrams) %>% 
  arrange(rater_id) %>%
  slice(1) %>%
  tabyl(n_diagrams) %>% 
  arrange(n_diagrams)

```


Create a category for studies with 1 to 7 diagrams or 8 to 12 diagrams


```{r}
sad_all <- sad_all %>% 
  mutate(n_diagram2 = case_when(n_diagrams < 8 ~ "1-7D",
                                TRUE ~ "8-12D"))

sad_all %>% 
  group_by(study, n_diagram2) %>% 
  arrange(rater_id) %>%
  slice(1) %>%
  tabyl(n_diagram2)

```


# Regression statistics 

## Remove outliers

We want to remove raters that are outliers using the criteria below 
 

Number of raters including outliers

```{r}
nrow(sad_all)
```

 
 
```{r}
sad_all2 <- sad_all %>% 
  filter(UN_r > 0.3) %>% 
  filter(SAD_r > 0.3) %>% 
  filter(UN_a < 30) %>% 
  filter(UN_a > -30) %>% 
  filter(SAD_a < 30) %>% 
  filter(SAD_a > -30) %>% 
  filter(UN_b < 5) %>% 
  filter(UN_b > -5) %>% 
  filter(SAD_b < 5) %>% 
  filter(SAD_b > -5) %>% 
  mutate(gain_r = SAD_r - UN_r) %>% 
  mutate(gain_a = SAD_a - UN_a) %>% 
  mutate(gain_b = SAD_b - UN_b)

# number of raters after outlier removal
nrow(sad_all2)

# Number of raters removed
nrow(sad_all)-nrow(sad_all2)

# Percentage of outliers
(nrow(sad_all)-nrow(sad_all2))/nrow(sad_all)*100

# Check now number of raters per study

sad_all2 %>%   group_by(study, pub_year) %>% 
  tabyl(study) %>% 
    arrange(n) 
```

Let's remove again studies with less than 6 raters

```{r}

sad_all2 %>% 
   group_by(study, pub_year) %>% 
  tabyl(study) %>% 
  arrange(n) 

sad_all2 <- sad_all2 %>% 
  filter(study != 79,
         study != 97, 
         study != 35,
         study != 62,
         study != 70 ,
         study != 103, 
                )
nrow(sad_all2)


# Number of studies
sad_all2 %>% group_by(study, pub_year) %>% 
  tabyl(study) %>% 
    arrange(n) %>% 
  count()

# write selected
sad_all2 %>% 
  tabyl(study) %>% 
  arrange(study) %>% 
  write_csv("selected_final.csv")
```



# Exploratory plots

## Precision

```{r}
p1_precision <- sad_all2 %>%
  select(study, rater_id, SAD_r, UN_r) %>% 
  gather(stats, value, 3:4) %>% 
  ggplot(aes(value, stats, fill = stats))+
  geom_density_ridges(scale = 3, alpha = 0.8)+
   geom_vline(xintercept = mean(sad_all2$UN_r), linetype =2, size=1, color = "darkorange")+ 
theme(legend.position = "none")+
theme_minimal()+  
  geom_vline(xintercept = mean(sad_all2$SAD_r), linetype =2, size=1, color = "black")+ theme(legend.position = "none")+
  scale_fill_colorblind()+
  labs(y = "", x ="Precision (r)")
```


```{r}
p2_precision <- sad_all2 %>%
  select(study, rater_id, gain_r) %>% 
  ggplot(aes(gain_r, fill = "gain_r"))+
  geom_density(alpha = 0.7)+
  geom_vline(xintercept = mean(sad_all2$gain_r), linetype =2, size=1, color = "darkorange")+ theme(legend.position = "none")+
  labs(x = "Gain in precision (r)")+
  scale_fill_colorblind()
```



```{r fig.height=4, fig.width=4}
p3_precision <- sad_all2%>% 
  ggplot()+
  theme_few()+
  #geom_jitter(width =0.1, color = "gray90")+
   coord_flip()+
  stat_summary(aes(factor(study), UN_r), fun.data = "mean_cl_boot", colour = "darkorange", size = 0.2)+
  stat_summary(aes(factor(study), SAD_r), fun.data = "mean_cl_boot", colour = "grey30", size = 0.2)+
    geom_hline(yintercept = median(sad_all2$UN_r), linetype =1, size=0.5, color = "darkorange")+
    geom_hline(yintercept = median(sad_all2$SAD_r), linetype =1, size=0.5, color = "grey30")+
  theme(axis.text.y=element_blank())+
  labs(x = "Study", y = "Precision (r)")

```


```{r fig.height=3, fig.width=3}

p4_precision <- sad_all2 %>%
  ggplot()+
  theme_few()+
  #geom_jitter(width =0.1, color = "gray90")+
   coord_flip()+
    stat_summary(aes(reorder(factor(study), gain_r), gain_r), fun.data = "mean_cl_boot", colour = "grey50", size = 0.2)+
   geom_hline(yintercept = mean(sad_all2$gain_r), linetype =2, size=0.5)+
     geom_hline(yintercept = 0, linetype =1, size=0.5)+
  labs(x = "", y = "Gain/loss (SAD_r - UN_r)")+
  
  theme(axis.text.y=element_blank())
```


```{r}
library(patchwork)
(p1_precision | p3_precision | p4_precision)+
 plot_annotation(tag_levels = 'A')
  ggsave("figs/P1_precision.png", width =8, height =3)
    
```



## Intercept


```{r}
p2_accuracy1 <- sad_all2 %>%
  select(study, rater_id, SAD_a, UN_a) %>% 
  gather(stats, value, 3:4) %>% 
  ggplot(aes(value, stats, fill = stats))+
  geom_density_ridges(scale = 6, alpha = 0.8)+
  scale_fill_colorblind()+
  labs(y = "", x = "Intercept (a)")+
  geom_vline(xintercept = 0, color = "gray50", linetype =2, size=1)+
  theme(legend.position = "none")+
   geom_vline(xintercept = mean(sad_all2$SAD_a), linetype =2, size=1, color = "black")+
  
   geom_vline(xintercept = mean(sad_all2$UN_a), linetype =2, size=1, color = "darkorange")

```



```{r fig.height=3, fig.width=3}
p2_accuracy2 <- sad_all2 %>%
  ggplot()+
  theme_few()+
  coord_flip()+
   stat_summary(aes(factor(study), UN_a), fun.data = "mean_cl_boot", colour = "darkorange", size = 0.2)+
  stat_summary(aes(factor(study), SAD_a), fun.data = "mean_cl_boot", colour = "grey30", size = 0.2)+
  geom_hline(yintercept = median(sad_all2$SAD_a, na.rm = TRUE), linetype =1, size=0.5, color = "grey30")+
    geom_hline(yintercept = median(sad_all2$UN_a, na.rm = TRUE), linetype =1, size=0.5, color = "darkorange")+
   
  labs(y = "Intercept", x = "")+
  
  theme(axis.text.y=element_blank())
  
```


```{r fig.height=3, fig.width=3}
p2_accuracy3 <- sad_all2 %>%
  ggplot()+
  theme_few()+

  #geom_jitter(width =0.1, color = "gray90")+
   coord_flip()+
    stat_summary(aes(reorder(factor(study), gain_a), gain_a), fun.data = "mean_cl_boot", colour = "grey50", size = 0.2)+
   geom_hline(yintercept = mean(sad_all2$gain_a, na.rm = TRUE), linetype =2, size=0.5)+
     geom_hline(yintercept = 0, linetype =1, size=0.5)+
  labs(x = "", y = "Constant bias (a) reduction ")+
  
  theme(axis.text.y=element_blank())
```



```{r}
plot_grid(p2_accuracy1, 
          p2_accuracy2,
          p2_accuracy3,
           ncol =3, align = "vh")
  ggsave("figs/P1_accuracy_a.png", width =8, height =3)
  
  (p2_accuracy1 | p2_accuracy2 | p2_accuracy3)+
 plot_annotation(tag_levels = list('D','E', 'F'))
  ggsave("figs/P1_accuracy_a.png", width =8, height =3)
    
```


## Slope

```{r}
p3_accuracy1 <- sad_all2 %>%
  select(study, rater_id, SAD_b, UN_b) %>% 
  gather(stats, value, 3:4) %>% 
  ggplot(aes(value, stats, fill = stats))+
  geom_density_ridges(scale = 6, alpha = 0.8)+
  scale_fill_colorblind()+
  labs(y = "", x = "Slope (b)")+
  theme(legend.position = "none")+
   geom_vline(xintercept = mean(sad_all2$SAD_b), linetype =1, size=1, color = "black")+
  geom_vline(xintercept = 1, color = "gray50", linetype =2, size=1)+
   geom_vline(xintercept = mean(sad_all2$UN_b), linetype =1, size=1, color = "darkorange")

```


```{r fig.height=3, fig.width=3}
p3_accuracy2 <- sad_all2 %>%
  ggplot()+
  theme_few()+
  coord_flip()+
   stat_summary(aes(factor(study), UN_b), fun.data = "mean_cl_boot", colour = "darkorange", size = 0.2)+
  stat_summary(aes(factor(study), SAD_b), fun.data = "mean_cl_boot", colour = "grey30", size = 0.2)+
  geom_hline(yintercept = median(sad_all2$SAD_b, na.rm = TRUE), linetype =1, size=0.5, color = "grey30")+
    geom_hline(yintercept = median(sad_all2$UN_b, na.rm = TRUE), linetype =1, size=0.5, color = "darkorange")+
   
  labs(y = "Slope", x = "")+
  
  theme(axis.text.y=element_blank())
  
```


```{r fig.height=3, fig.width=3}
p3_accuracy3 <- sad_all2 %>%
  ggplot()+
  theme_few()+

  #geom_jitter(width =0.1, color = "gray90")+
   coord_flip()+
    stat_summary(aes(reorder(factor(study), gain_b), gain_b), fun.data = "mean_cl_boot", colour = "grey50", size = 0.2)+
   geom_hline(yintercept = mean(sad_all2$gain_b, na.rm = TRUE), linetype =2, size=0.5)+
     geom_hline(yintercept = 0, linetype =1, size=0.5)+
  
  labs(x = "", y = "Systematic bias (b) reduction ")+
  
  theme(axis.text.y=element_blank())
```



```{r}
plot_grid(p3_accuracy1, 
          p3_accuracy2,
          p3_accuracy3,
           ncol =3, align = "vh")
  ggsave("figs/P3_accuracy_b.png", width =8, height =3)
  
  
  p <- (p1_precision | p3_precision | p4_precision)/
  (p2_accuracy1 | p2_accuracy2 | p2_accuracy3)/
  (p3_accuracy1 | p3_accuracy2 | p3_accuracy3)   
  p + plot_annotation(tag_levels = 'A')
    ggsave("figs/all_accuracy_precision.png", width =8, height =8)
  
  
```

# Random effects meta-analysis 


## Data preparation

```{r}
dat_ma <- sad_all2 %>% 
  select(study, rater_id, organ2, n_diagram2, HB, pathogen_group, diag_type, col_type, lesion_number, min_sev, max_sev, n_diagrams, UN_r, SAD_r, UN_a, SAD_a, UN_b, SAD_b, Symptom_code2) %>% 
  mutate(rater_class = case_when(UN_r > 0.92 ~ "Good",
                                 UN_r < 0.78 ~ "Poor",
                                 TRUE ~ "Fair")) %>% 
  gather(stats, value, 13:18) %>% 
  mutate(value = as.numeric(value))


dat_ma2 <- dat_ma %>% 
  group_by(study,organ2, n_diagram2, HB, pathogen_group,
           diag_type, col_type, lesion_number, min_sev,
           max_sev, n_diagrams,  stats, Symptom_code2) %>% 
  summarize(yi = mean(value),
            vi = var(value),
            n = n())

dat_ma2 <- dat_ma2 %>% 
  separate(stats, c("Method", "stat"), remove = FALSE) %>% 
   mutate(max_sev_class = case_when(
             max_sev > 50 ~ "maxsev > 50%",
              TRUE ~ "max_sev < 50%"
                        )) 


```

## Correlation coefficient


```{r}
dat_r2 <- dat_ma2 %>% 
  filter(stat == "r")

dat_r2 %>% 
  ggplot(aes(yi))+
  geom_histogram()

library(metafor)

meta_r <- rma.mv(yi, vi/n,
  mods = ~Method,
  random = list(~ Method | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = dat_r2
)

meta_r2 <- rma.mv(yi, vi/n,
  mods = ~Method*Symptom_code2 ,
  random = list(~ Method | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = dat_r2
)
anova(meta_r , meta_r2)
anova(meta_r2, btt = c(6,7,8))


r <- tibble::tribble(
  ~method,  ~mean,   ~cil,   ~ciu,
    "SAD", 0.9430, 0.9339, 0.9522,
     "UN", 0.8716, 0.8496, 0.8935
  )

library(cowplot)
library(ggthemes)
rp <- r %>% 
  ggplot(aes(method, mean, color = method))+
  geom_point()+
  geom_errorbar(aes(ymin = cil, ymax = ciu), width =0.1)+
  ylim(0.80, 1.05)+
  theme_few()+

  theme(legend.position = "none")+
  scale_color_manual(values = c("grey30", "darkorange"))+
  labs(y = "Pearson's r", 
         x = "")

```

## Intercept


```{r}
dat_a <- dat_ma2 %>% 
  filter(stat == "a")

dat_a %>% 
  ggplot(aes(yi))+
  geom_histogram()

meta_a <- rma(yi, sqrt(vi), 
              mods = ~ Method -1 ,
                data = dat_a, method = "ML")

meta_a2 <- rma.mv(yi, vi/n,
  mods = ~Method-1,
  random = list(~ Method | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = dat_a
)
a <- tibble::tribble(
  ~method,  ~mean,   ~cil,   ~ciu,
    "SAD", 0.7610, 0.4899, 1.0322,
     "UN", 3.4173, 2.7880, 4.0465
  )

ap <- a %>% 
  ggplot(aes(method, mean, color = method))+
  geom_point()+
  geom_errorbar(aes(ymin = cil, ymax = ciu), width =0.1)+
   theme_few()+
    geom_hline(yintercept = 0)+
  theme(legend.position = "none")+
  scale_color_manual(values = c("grey30", "darkorange"))+
    labs(y = "Intercept" , 
         x = "")+
  ylim(-0.6, 4.5)
```



## Slope


```{r}
dat_b <- dat_ma2 %>% 
  filter(stat == "b")

dat_b %>% 
  ggplot(aes(yi))+
  geom_histogram()

meta_b <- rma(yi, sqrt(vi), 
              mods = ~ Method-1 ,
                data = dat_b, method = "ML")

meta_b2 <- rma.mv(yi, vi/n,
  mods = ~Method-1,
  random = list(~ Method | study),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = dat_b
)

b <- tibble::tribble(
  ~method,  ~mean,   ~cil,   ~ciu,
    "SAD", 0.9665, 0.9147, 1.0183,
     "UN", 1.0960, 1.0089, 1.1830
  )

bp <- b %>% 
  ggplot(aes(method, mean, color = method))+
  geom_point()+
  geom_errorbar(aes(ymin = cil, ymax = ciu), width =0.1)+
  theme_few()+
    geom_hline(yintercept = 1)+
  theme(legend.position = "none")+
  scale_color_manual(values = c("grey30", "darkorange"))+
  ylim(0.8, 1.2)+
    labs(y = "Slope", 
         x = "")

```



## Plots


```{r}
theme_set(theme_light())
x <- c(0:100)
y <- c(0:100)
dat <- data.frame(x,y)
UN_p1 <- dat %>% 
  ggplot(aes(x, y))+
  coord_fixed()+
  geom_point(color = "NA")+
  geom_abline(intercept = 0, slope = 1, color="grey", 
                 linetype="solid", size=1)+
  geom_abline(intercept = 3.417, slope = 1.096, color="darkorange", 
                 linetype="solid", size=1)+
  geom_abline(intercept = 2.788, slope = 1.0089, color="darkorange", 
                 linetype="dashed", size=1)+
  geom_abline(intercept = 4.0465, slope = 1.1830, color="darkorange", 
                 linetype="dashed", size=1)+
    xlim(0,20)+
  ylim(0,20)+
    theme_few()+
  labs(x ="Actual severity (%)",
       y = "Estimate severity (%)", 
       title = "Unaided")
 
```


```{r}
SAD_p1 <- dat %>% 
  ggplot(aes(x, y))+
  coord_fixed()+
  geom_point(color = "NA")+
  geom_abline(intercept = 0, slope = 1, color="grey", 
                 linetype="solid", size=1)+
  geom_abline(intercept = 0.7610, slope = 0.9665, color="grey30", 
                 linetype="solid", size=1)+
  geom_abline(intercept = 0.4899, slope = 0.9147, color="grey30", 
                 linetype="dashed", size=1)+
  geom_abline(intercept = 1.0322, slope = 1.0183, color="grey30", 
                 linetype="dashed", size=1)+
        theme_few()+
   xlim(0,20)+ 
  ylim(0,20)+
  labs(x ="Actual severity (%)",
       y = "Estimate severity (%)", 
       title = "SAD")


```

## multipanel

```{r}
library(patchwork)

  g1 <- (ap / bp / rp)
    
  g2 <-  (UN_p1 / SAD_p1)
  
(g1 |  g2) + plot_annotation(tag_levels = 'A')
  ggsave("figs/plot_all.png", width = 6, 
         height = 7)

```


# Prepare for MCA 

```{r}
sad_mv <- sad_all2 %>%
  group_by(study) %>% 
  summarize(mean_Ur = mean(UN_r),
            var_Ur = sd(UN_r)^2,
            mean_Ar = mean(SAD_r),
            var_Ar = sd(SAD_r)^2, 
            
            mean_Ua = mean(UN_a),
            var_Ua = sd(UN_a)^2, 
            
            mean_Aa = mean(SAD_a),
            var_Aa = sd(SAD_a)^2, 
            
            mean_Ub = mean(UN_b),
            var_Ub = sd(UN_b)^2, 
            
            mean_Ab = mean(SAD_b),
            var_Ab = sd(SAD_b)^2 
            )

sad_mv <- left_join(sad_mv, sad_all2)



```

### Define categories


```{r}
sad_mv <- sad_mv %>% 
  #select(organ2, diag_type2, n_diagram2, Kind_of_lesion, lesion_number, lesion_pattern, lesion_shape, coalesc, Kind_of_organ, max_sev_class) %>% 
  mutate(SAD_r = case_when(
        mean_Ar > 0.92 ~"r > 0.92",
    mean_Ar < 0.84 ~ "r < 0.84", 
    TRUE  ~ "r 0.84 to 0.92"
  ) ) %>% 
    
  mutate(UN_r = case_when(
    mean_Ur > 0.92 ~"r > 0.92",
    mean_Ur < 0.84 ~ "r < 0.84", 
    TRUE  ~ "r 0.84 to 0.92"
  ) ) %>% 
  
 mutate(SAD_a = case_when(
    mean_Aa > 3.4  ~"a > 3.4",
    TRUE < -3.4  ~"a < -3.4"
  ) ) %>% 
    
  mutate(UN_a = case_when(
     mean_Ua > 3.4  ~"a > 3.4",
          TRUE  ~ " a < 3.4"
  ) ) %>% 
   mutate(SAD_b = case_when(
    mean_Ab > 1 ~  "b > 1",
       TRUE ~ "b < 1")) %>% 
  
       mutate(UN_b = case_when(
    mean_Ub > 1 ~  "b > 1",
     TRUE ~ "b < 1")) %>% 
  
       mutate(max_sev_class = case_when(
    max_sev > 50 ~  "max_sev > 50%",
     TRUE ~ "max_sev <= 50%")) 
  
  

          
```



# UNAIDED ESTIMATES 





```{r}
library(FactoMineR)


sad_mv2 <- sad_mv %>% 
  group_by(study) %>% 
slice(1)

sad_mv2 <- sad_mv2 %>% 
filter(lesion_number != "Single")

attach(sad_mv2)
dat_mca2 <- data.frame(
  sad_mv2$UN_a,
  sad_mv2$UN_b,
  sad_mv2$UN_r,
  sad_mv2$Symptom_code2,
  sad_mv2$max_sev_class,
  sad_mv2$organ2
  )
detach(sad_mv2)

cats <- apply(dat_mca2, 2, function(x) nlevels(as.factor(x))) # enumera as categorias
mca1 <- MCA(dat_mca2, graph = TRUE)
res.mca <- MCA(dat_mca2, graph = FALSE)
library("factoextra")
eig.val <- get_eigenvalue(res.mca)
head(eig.val)
fviz_screeplot(res.mca, addlabels = TRUE, ylim = c(0, 45))
fviz_cos2(res.mca, choice = "var", axes = 1:2)
cont_dim1 <- fviz_contrib(res.mca, choice = "var", axes = 1, top = 15)
cont_dim2 <- fviz_contrib(res.mca, choice = "var", axes = 2, top = 15)
cont_dim12 <- fviz_contrib(res.mca, choice = "var", axes = 1:2, top = 15)
p <- fviz_mca_var(res.mca,
  label = "var", repel = T,
 col.var =  "contrib",
  ggtheme = theme_light()
)+  scale_color_continuous(low = "black", high = "#E69F00") +
  theme(legend.position = "right")+
  labs(color = expression(cos^{2}, title = ""))
p1 <- plot_grid(cont_dim1, cont_dim2, ncol = 1, align = "vh")
p0 <- plot_grid(p, labels = LETTERS, ncol =1, align = "vh", rel_widths  = c(1.1, 0.8))
  ggsave("figs/MCA_plot_unaided.png", width =6, height =5)
  
```


## Univariate exploratory

## Effect of symptom code

```{r}
library(ggthemes)
p1 <- sad_mv2 %>% 
  ggplot(aes(Symptom_code2, mean_Ur))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3)+
   geom_hline(yintercept = 0.905, linetype = "dashed")+
  labs(x = "", 
       y = "Pearson's r")+
  theme_few()

p2 <- sad_mv2 %>% 
  ggplot(aes(Symptom_code2, mean_Ua))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed")+
    labs(x = "", 
       y = "Intercept")+
    theme_few()

p3 <- sad_mv2 %>% 
  ggplot(aes(Symptom_code2, mean_Ub))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3) +
  geom_hline(yintercept = 1, linetype = "dashed")+
    labs(x = "", 
       y = "Slope")+
    theme_few()

p01 <- (p1 | (p2 / p3))

```




## Effect of max_sev


```{r}
p4 <- sad_mv2 %>% 
  ggplot(aes(max_sev_class, mean_Ur))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3)+
   geom_hline(yintercept = 0.905, linetype = "dashed")+
      labs(x = "", 
       y = "Pearson's r")+
    theme_few()

p5 <- sad_mv2 %>% 
  ggplot(aes(max_sev_class, mean_Ua))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed")+
      labs(x = "", 
       y = "Intercept")+
    theme_few()

p6 <- sad_mv2 %>% 
  ggplot(aes(max_sev_class, mean_Ub))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3) +
  geom_hline(yintercept = 1, linetype = "dashed")+
      labs(x = "", 
       y = "Slope")+
    theme_few()

p02 <- (p4 | (p5 / p6))

```




## Effect of organ (leaf x other)


```{r}
p7 <- sad_mv2 %>% 
  ggplot(aes(organ2, mean_Ur))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3)+
   geom_hline(yintercept = 0.905, linetype = "dashed")+
      labs(x = "", 
       y = "Pearson's r")+
    theme_few()

p8 <- sad_mv2 %>% 
  ggplot(aes(organ2, mean_Ua))+
  geom_boxplot(outlier.colour = NA, fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed")+
      labs(x = "", 
       y = "Intercept")+
    theme_few()

p9 <- sad_mv2 %>% 
  ggplot(aes(organ2, mean_Ub))+
  geom_boxplot(outlier.colour = NA,fill = "darkorange", alpha = 0.8)+
  geom_jitter(width = 0.1, alpha = 0.3) +
  geom_hline(yintercept = 1, linetype = "dashed")+
      labs(x = "", 
       y = "Slope")+
    theme_few()

p03 <- (p7 | (p8 / p9))

```

## plots

```{r}
(p01 / p02 ) + plot_annotation(tag_levels = 'A')
ggsave("figs/boxplots_unaided.png", width = 6, height = 8)

```



# AIDED ESTIMATES 


## Univariate exploratory

### Effect of inherent coefficients

```{r}
p20 <- sad_mv2 %>% 
  ggplot(aes(mean_Ur, mean_Ar-mean_Ur, color = Symptom_code2))+
 geom_point(size = 2, alpha = 0.7)+
  #geom_smooth(method = "lm", se = F )+
   geom_hline(yintercept = 0, linetype = "solid")+
  geom_hline(yintercept = 0.05, linetype = "dashed")+
      labs( 
       y = "Gain/loss in Precision",
       x = "Unaided Precision (Pearson's r)")+
  scale_color_colorblind()+
    theme_few()+
  theme(legend.position = "none")

```

```{r}
p21 <- sad_mv2 %>% 
  ggplot(aes(mean_Ua, mean_Aa-mean_Ua, color = Symptom_code2))+
 geom_point(size = 2, alpha = 0.7)+
  #geom_smooth(method = "lm", se = F )+
   geom_hline(yintercept = 0, linetype = "solid")+
 
      labs( 
       y = "Intercept value reduction",
       x = "Unaided intercept")+
  scale_color_colorblind()+
    theme_few()+
  theme(legend.position = "none")
```

```{r}

p22 <- sad_mv2 %>% 
  ggplot(aes(mean_Ub, mean_Ab - mean_Ub, color = Symptom_code2))+
 geom_point(size = 2, alpha = 0.7)+
 geom_hline(yintercept = 0, linetype = "solid")+

      labs( 
       y = "Slope value reduction",
       x = "Unaided Slope", 
       color = "N. of lesions")+
  scale_color_colorblind()+
    theme_few()

```

```{r}
(p20 | (p21  / p22)) +
   plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = 'A')
ggsave("figs/inherent_ability.png", width = 9, height = 5)
```


### Effect of SAD color

```{r}

p41 <- sad_mv2 %>% 
  ggplot(aes(diag_type2, mean_Ar - mean_Ur))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
  geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Gain/loss in Precision",
       x = "")+
    theme_few()

p42 <- sad_mv2 %>% 
  ggplot(aes(diag_type2, mean_Aa - mean_Ua))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
  geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Intercept reduction",
       x = "")+
    theme_few()

p43 <- sad_mv2 %>% 
  ggplot(aes(diag_type2, mean_Ab - mean_Ub))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
  geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Slope reduction",
       x = "")+
    theme_few()

p_sadtype <- p41 | (p42/p43)

```

### Effect of n_diagram

```{r}

p51 <- sad_mv2 %>% 
  ggplot(aes(n_diagram2, mean_Ar - mean_Ur))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
   geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Gain/loss in Precision",
       x = "")


p52 <- sad_mv2 %>% 
  ggplot(aes(n_diagram2, mean_Aa - mean_Ua))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Intercept reduction",
       x = "")


p53 <- sad_mv2 %>% 
  ggplot(aes(n_diagram2, mean_Ab - mean_Ub))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Slope reduction",
       x = "")

p_ndiag <- p51 | (p52/p53)

(p_sadtype /  p_ndiag) + plot_annotation(tag_levels = 'A')
ggsave("figs/diag_effects.png", width =7, height = 8)

```



### Effect of symptom type

```{r}

p61 <-sad_mv2 %>% 
  ggplot(aes(Symptom_code2, mean_Ar - mean_Ur))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Gain/loss in Precision",
       x = "")

p62 <- sad_mv2 %>% 
  ggplot(aes(Symptom_code2, mean_Aa - mean_Ua))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Intercept reduction",
       x = "")



p63 <- sad_mv2 %>% 
  ggplot(aes(Symptom_code2, mean_Ab - mean_Ub))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Slope reduction",
       x = "")


p_symptomcode <- p61 | (p62/p63)



```

### Effect of severity max

```{r}

p71 <- sad_mv2 %>% 
  ggplot(aes(max_sev_class, mean_Ar - mean_Ur))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Gain/loss in Precision",
       x = "")

p72 <- sad_mv2 %>% 
  ggplot(aes(max_sev_class, mean_Aa - mean_Ua))+
 geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Intercept reduction",
       x = "")

p73 <- sad_mv2 %>% 
  ggplot(aes(max_sev_class, mean_Ab - mean_Ub))+
geom_boxplot(outlier.colour = NA, fill = "grey30", alpha = 0.8)+
  geom_jitter(width =0.1, alpha = 0.3)+
    theme_few()+
    geom_hline(yintercept = 0, linetype = "dashed")+
     labs( 
       y = "Slope reduction",
       x = "")


p_sevmax <- p71 | (p72/p73)


(p_symptomcode /  p_sevmax) + plot_annotation(tag_levels = 'A')
ggsave("figs/symptom_effects.png", width =7, height = 8)

```

# DESCRIPTION OF STUDIES

```{r}
p81 <- sad_mv2 %>% 
  ggplot(aes(pub_year, fill = organ2))+
  geom_bar()+
  theme_minimal_hgrid()+
  scale_fill_grey()+
  scale_y_continuous(n.breaks = 11)+
  labs(x = "Publication year", 
       fill = "Organ")
```

```{r}

p82 <- sad_mv2 %>% 
  ggplot(aes(reorder(study, max_sev)))+
  geom_errorbar(aes(ymin = min_sev, ymax = max_sev))+
  theme_minimal_vgrid()+
  coord_flip()+
  labs(x = "Study number",
       y = "SADs severity range")
  

```


```{r}

p83 <- sad_mv2 %>% 
  group_by(diag_type2) %>% 
  count() %>% 
  ggplot(aes(diag_type2, n, fill = diag_type2))+
  geom_col()+
    theme_minimal_hgrid()+
  scale_fill_grey()+
  theme(legend.position = "none")+
  scale_y_continuous(n.breaks = 11, limits = c(0,65))+
    labs(x = "SADs diagram type",
       y = "Count")

  
```


```{r}
p84 <- sad_mv2 %>% 
  group_by(n_diagrams) %>% 
  count() %>% 
  ggplot(aes(n_diagrams, n))+
  geom_col()+
    theme_minimal_hgrid()+
  scale_fill_grey()+
  scale_y_continuous(n.breaks = 8)+
  scale_x_continuous(n.breaks = 30)+
   labs(x = "Number of diagrams in the SADs",
       y = "Count")
  
```

## multipanel

```{r}

((p81 + p82) / (p83 + p84)) + plot_annotation(tag_levels = 'A')
ggsave("figs/description_studies.png", width = 14, height = 12)

```

# TABLES


```{r}
sad_mv2 %>% 
  select(pub_year, author, crop, organ, dis_name, diag_type, n_diagrams, max_sev, Symptom_code2) %>% 
  writexl::write_xlsx("table_70studies.xlsx")


```

